\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-06-13 latex_corrected_anonymous/UMEM_CoSim.tex
finished paper and resubmitted!

\author{Clayton Miller\textsuperscript{a,b}%
$^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
Daren Thomas\textsuperscript{b},
J\'er\^ome K\"ampf\textsuperscript{c},
and Arno Schlueter\textsuperscript{b}\\
\vspace{6pt}
\textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
\textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
\textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
}

>>>>

% \author{Clayton Miller\textsuperscript{a,b}%
% $^{\ast}$\thanks{$^\ast$Corresponding author. Email: clayton@nus.edu.sg}, 
% Daren Thomas\textsuperscript{b},
% J\'er\^ome K\"ampf\textsuperscript{c},
% and Arno Schlueter\textsuperscript{b}\\
% \vspace{6pt}
% \textsuperscript{a}{\em Department of Building, School of Design and Environment, National University of Singapore, 117566 Singapore};\\
% \textsuperscript{b}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
% \textsuperscript{c}{\em ENERGY Institute, HEIA-FR / HES-SO Fribourg, Bd Perolles 80, 1750 Fribourg, Switzerland}
% }
